% EDUCACION REGLADA
\section{\textsc{Education}}
\cventry{2015 -- 2017\\unfinished}{Ph.D. High-Performance Computing}{(Performed two years of studies in pursuit of PhD before exiting program)}{Universitat Aut\`onoma de Barcelona (UAB)}{Spain}{}
%Mathematics, Department of Mathematics, Foo Baz University, BB, (Performed four years of studies in pursuit of PhD before exiting program) August 2011 – March 2015

\cventry{2013 -- 2014}{M.Sc. High-Performance Computing, Information Theory and Security}
{}{Universitat Aut\`onoma de Barcelona (UAB)}{Spain}
{UK Framework: RQF Level 7 - Master's degree}

\cventry{2007 -- 2011}{BSc. Computer Engineering}
{}{Universitat Aut\`onoma de Barcelona (UAB)}{Spain}
{UK Framework: RQF Level 7 - Integrated Master's degree (MEng)}

\cventry{2002 -- 2005}{ASc. Computer Engineering}
{(ASc.'s extraordinary award)}{Universitat Aut\`onoma de Barcelona (UAB)}{Spain}{UK Framework: RQF Level 6 - Bachelor degree}

\subsection{Certifications}
\cventry{2021}{Professional Cloud Architect (PCA)}{Gloogle Cloud}{}
{Credencial ID: 27766334}{}

\cventry{2020}{Professional Scrum Master I (PSM I)}{Scrum.org}{}
{Certified Scrum Master}
{Credencial ID: 59206}{}

\cventry{2019}{FitSM® Foundation}{APMG International}
{}{Credencial ID: 04309561-01-VZWJ}{}

\subsection{Courses}


\cventry{2021}{OpenStack User and Administration Workshop with Kayobe}{Introduction to Kayobe operations and advanced administration. Administering CEPH storage with OpenStack. Bare metal deployment with Ironic. Security Audit with Wazuh.}{}{Astrazeneca PLC}{3rd-Party delivered course by StackHPC Ltd}{}

\cventry{2021}{Hashicorp Workshops and Trainings}{Training 101 workshops around Terraform, Consul, Vault and Nomad. Introduction, Best Practises, Enterprise Overview. Multi-DC Service Discovery, Service Mesh and Vault Replication. Multi-Region Federation with Consul and Nomad}{}{Astrazeneca PLC}{3rd-Party delivered course by HashiCorp}{}

\cventry{2021}{Be the Manager People Won't Leave}{LinkedIn Learning}{Manager relationships are becoming the make-or-break point for whether employees stay or go. Basics how to be someone people can trust, be an example of integrity, and be relentlessly inclusive}{}{}

\cventry{2021}{Developing Teams}{Learn more about Developing Teams}{As a people leader, how to develop and build and effective team. How to build trust and loyalty and improve group dynamics}{}{} 

\cventry{2021}{People Manager: New to AZ}{Manager Essentials}{
This pathway is designed to enable you to set yourself and others up for success. To grow, coach and support your people to be an effective team}{}{}

\cventry{2021}{Leading People}{AZ Leadership Training Program}{Leading People is a CEO Award winning programme designed specifically for AstraZeneca. Each topic combines a core Leadership skill with a core AZ topic or theme}{}{}

\cventry{2021}{Helm Deep Dive v3}{A Cloud Guru}{}{}{}

\cventry{2021}{Google Cloud SRE and DevOps Engineer with Google Cloud Specialization}{Coursera}
{}{\href{https://coursera.org/share/b8a3e4c98cb6f52124c3b1e116602e92}{Certificate link}}{}

\cventry{2021}{Preparing for the Google Cloud Professional Cloud Architect Exam}{Coursera}
{}{\href{https://coursera.org/share/5504cfa0d565dd528d94e9291c228d77}{Certificate link}}{}

\cventry{2021}{Mastering the AWS Well-Architected Framework}{A Cloud Guru}{}{}{}

\cventry{2021}{Reliable Google Cloud Infrastructure: Design and Process}{Coursera}{}{}{}

\cventry{2021}{Leading Self}{AZ IT Leadership Training Program}{}{}{}

\cventry{2020}{Splunk Fundamentals Levels 1\&2}{Splunk Training}{}{}{}


% Dear Colleague
 
% We will be running an IT Cohort of the Global AZ Leading Self programme in April > June. You might be new and straight into a line manager role and therefore have also received an invite to the Leading People programme in which case you can watch the animations and consider which best aligns to your current IDP/discuss with your line manager. Given the circumstances and pressures just now, we are aware this will only be good timing for some, so please only register if it is appropriate for you to do so at this time.
 
% An overview of Leading Self
% Aimed at: Individual contributors seeking personal development.
% Programme Summary:
% A self-guided virtual programme with IT Sponsors and Mentors hosting live calls.
% Topics include; values & vision, self-confidence, resilience, unconscious bias, active listening, giving feedback, career planning & self-development.
% Run over 6 consecutive weeks starting 26th April 2021; you will be expected to engage with the content weekly and join a call with your group Mentor.
% Leading Self was launched in 2017 and to date over 8,000 AZ employees have taken part.
 
% Please discuss your attendance with your Line Manager in line with your IDP, if you book yourself on to the programme there is an expectation that you are fully committed to completing the 6-week programme.
 
% This is a great opportunity to apply theory while you work, learn from peers and IT Leaders, and you will have ongoing access to the fantastic content after programme completion.
 
 

\cventry{2019}{ISO-27001 foundation training}{Introduction to the concept of an ISMS and the ISO27001 process and standard}{}{Universisty of Cambridge}{3rd-Party delivered course.}{}

%LinkedIn learning

%Drupal: Migration from Falcon On Plone - An Introduction, Mon 30 Jul 2018, University Information Services Training.
%Learning REST APIs, Completed on Sep 16, 2018
%Skills: Back-End Web Development, Front-end Development
%DevOps Foundations: DevSecOps, Completed on Sep 15, 2018
%Skills: JIRA, Docker Products
%Advanced Python, Completed on Sep 30, 2018
%Skill: Python (Programming Language)
%Learning Kubernetes, Completed on Oct 5, 2018
%Advanced Cloud Native Go, Completed on Oct 15, 2018
%Skill: Go (Programming Language)
%Designing RESTful APIs, Completed on Oct 15, 2018
%Skills: Software Design, Back-End Web Development
%Lloc: Sala de Graus de l'Escola d'Enginyeria de la UAB

%* 2016-09-05/06/07

\cventry{2016}{Biostatistics and basic R for molecular biology analyses}{Simon Andrews (Head of Bioinformatics) and Anne Segonds-Pichon (Bio-Statistician), Babraham Bioinformatics}{Center for Research in Agricultural Genomics (CRAG)}{}{September 5th-7th, 2016 - Barcelona, Spain}{}

\cventry{2016}{(CSUC) IEEE Authors Workshop}{ Eszter Lucas - European Manager IEEE Client services}{}{Aula Màster - UPC, Campus Nord}{June 23th, 2016 - Barcelona, Spain}{}

\cventry{2016}{Network analysis and modeling in Cytoscape}{Dr. Marti Bernardo-Faura - Head of data analysis area}{}{Bioinformatics Core Unit, Center for Research in Agricultural Genomics (CRAG)}{June 16th, 2016}{}

\cventry{2016}{Galaxy DevOps Workshop 2016}{de.NBI, ELIXIR}{}{Institut fur Pharmazie und Molekulare Biotechnologie (IPMB)}{April 6-7th, 2016 - Heidelberg, Germany}{}
\cventry{2016}{PATC Course: Big Data Analytics}{PRACE}{}{BSC-UPC}{February 8-11, 2016 - Barcelona}{}
\cventry{2015}{Parallel computing and GPU computing}{Carlo Nardone}{NVidia Architect}{}{}{}
\cventry{2014}{Openstack Bootcamp OS110}{Dr. Damian Igbe}{Mirantis}{}{}{}



%\subsection{Courses}
% Add Fatwire, Drupal 2012
% Add socorrismo curso 2011
% Add Blender curso 2011
%\cventry{2006--2007}{Curso avanzado de administración de sistemas GNULinux}{Centro de Combinatoria y Comunicación Digital}{Universitat Autònoma de Barcelona}{(UAB)}{}{}
%\cventry{2005}{Curso de desarrollo de aplicaciones en J2EE}{Propia empresa}{Agresso Spain, SL}{}{}{}
%\cventry{2005}{Programación Lotus Domino}{Propia empresa}{Agresso Spain, SL}{}{}{}
%\cventry{2004}{Seguridad en intranets Linux}{Centro de Combinatoria y Comunicación Digital}{Universitat Autònoma de Barcelona}{(UAB)}{}{}
%\cventry{2004}{Introducción a la construcción de robots autónomos}{Universitat Autònoma de Barcelona}{(UAB)}{}{}
%\cventry{2000}{Curso especialización en banco de trabajo FSA560}{Robert Bosch España, S.A.}{}{}{}
%\cventry{2000}{Curso responsable de taller de mecánica y electricidad}{FORCEM}{}{}{}
%\cventry{1999}{Técnico Especialista en inyección electrónica Gasolina}{Neotec Sistemas, S.L.}{}{}{}
%\cventry{1999}{Curso especialización en osciloscopio digital}{Neotec Sistemas, S.L.}{}{}{}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}
%\close